SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-14 docs/questioning.tex
added POI attacks

{\sc html} is another {\sc dsl} that can be used for malicious
purposes when an application does not properly handle user-supplied
data. Based on this vulnerability attackers can supply valid {\sc
  html}, typically via a parameter value, and inject their own content
into the page. {\sc html} injection is mainly associated with {\sc
  xss} attacks~\cite{BJM08,LZRL09}. However, it can also be used as a
vehicle for cross-site request forgery ({\sc csrf}) attacks in the
following manner: Consider a bulletin board system where
{\tt img} tags are not checked. A malicious user could embed a {\sc
  csrf} request within an {\tt img} tag in the following manner:

@@

>>>>

{\sc html} is another {\sc dsl} that can be used for malicious
purposes when an application does not properly handle user-supplied
data. Based on this vulnerability attackers can supply valid {\sc
  html}, typically via a parameter value, and inject their own content
into the page. {\sc html} injection is mainly associated with {\sc
  xss} attacks~\cite{BJM08,LZRL09}. An {\sc xss} attack based on
{\sc html} injection though, can also be used as a
vehicle for a {\sc csrf} attack. Consider a bulletin board system where
{\tt img} tags are not checked. A malicious user could embed a {\sc
  csrf} request within an {\tt img} tag in the following manner:

@@

A recent attack called {\sc php} Object Injection
({\sc poi})~\cite{DKH14} does not directly involve code
injection and is performed by injecting malicious
payloads (for example cookies) that when deserialized
by the application, arbitrary code execution can be
achieved. Note that the exploitation model that we propose
in the following Section can represent such attacks too.
